Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-01-05 vertical-thermal-review.Rmd
addressing comments on l. 206-207
l. 206-207 'Leaves are typically warmer than air … '. That is not what is predicted in theory, proven by parts of the simulations in Fig. 3. Why not use 'Leaves can be warmer …'? That would be more consistent.
table 1 comments addressed
Table 1: What is here is not leaf gas exchange, and it seems that the authors have repeated the caption for Table 2 in error. Please fix this. Also don’t capitalise ‘leaf’.

$T_{leaf}$ is strongly tied to $T_{air}$, and is further influenced by other micrometeorological drivers (section 1) and by leaf traits and stomatal conductance (see sections 3-4). Leaves adjust to their environment to approach, when possible, an optimal $T_{leaf}$ for carbon assimilation and metabolic processes [@michaletzPlantThermoregulationEnergetics2015; @perezPhotosyntheticHeatTolerances2020; @drakeNoEvidenceHomeostatic2020]. 
Therefore, leaves are typically cooler than the air at night, and under some daytime conditions (cloudy skies, high wind speeds, and high $T_{air}$). 
Leaves are typically warmer than air when under full sunlight, especially under slow wind speeds and low $T_{air}$ [@doughtyAreTropicalForests2008].
While $T_{leaf}$ is rarely exactly equal to $T_{air}$, it is most commonly within a few degrees [@cavaleriColdbloodedForestsWarming2020].

@@

\newpage
**Table `r table_leaf_traits`.** Summary of observed variation in Leaf gas exchange and its thermal sensitivity across the vertical gradient and/or between sun and shade leaves. Studies listed here were compiled using a systematic review process, as described in Supplementary Information Methods `r appendix_lit_review_methods`.

>>>>

$T_{leaf}$ is strongly tied to $T_{air}$, and is further influenced by other micrometeorological drivers (section 1) and by leaf traits and stomatal conductance (see sections 3-4). Leaves adjust to their environment to approach, when possible, an optimal $T_{leaf}$ for carbon assimilation and metabolic processes [@michaletzPlantThermoregulationEnergetics2015; @perezPhotosyntheticHeatTolerances2020; @drakeNoEvidenceHomeostatic2020]. 
Therefore, leaves are typically cooler than the air at night, and under some daytime conditions (cloudy skies, high wind speeds, and high $T_{air}$). 
Leaves can be warmer than air when under full sunlight, especially under slow wind speeds and low $T_{air}$ [@doughtyAreTropicalForests2008].
While $T_{leaf}$ is rarely exactly equal to $T_{air}$, it is most commonly within a few degrees [@cavaleriColdbloodedForestsWarming2020].

@@

\newpage
**Table `r table_leaf_traits`.** Summary of typically observed variation in leaf traits its thermal sensitivity across the vertical gradient and/or between sun and shade leaves. Studies listed here were compiled using a systematic review process, as described in Supplementary Information Methods `r appendix_lit_review_methods`.
